%==============================================================================
% Structural Robustness of Isotropic S³ Vacua in Einstein–Cartan
% Minisuperspace via Chiral Equilibrium and Weyl Stability
%==============================================================================
\documentclass[12pt,a4paper]{article}

%------------------------------------------------------------------------------
% Packages
%------------------------------------------------------------------------------

% Fonts / encoding (helps text extraction)
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{textcomp}
\usepackage[final]{microtype}

% Math
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{mathtools}
\usepackage{bm}

% Graphics and figures
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}

% TikZ for diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc, fit, backgrounds}

% Layout and formatting
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

% Misc (xcolor should come before hyperref)
\usepackage{xcolor}
\usepackage{enumitem}

% References and links
\definecolor{linkblue}{RGB}{0,0,180}
\usepackage[colorlinks=true,linkcolor=linkblue,citecolor=linkblue,urlcolor=linkblue]{hyperref}
\usepackage{cleveref}

% Code listings (for appendices)
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  language=Python
}

% section break
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}

%------------------------------------------------------------------------------
% Theorem environments
%------------------------------------------------------------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

%------------------------------------------------------------------------------
% Custom commands
%------------------------------------------------------------------------------
% Math shortcuts
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Veff}{V_{\mathrm{eff}}}
\newcommand{\VEC}{V_{\mathrm{EC}}}
\newcommand{\VWeyl}{V_{\mathrm{Weyl}}}
\newcommand{\Ric}{R}
\newcommand{\LC}{\mathrm{LC}}
\newcommand{\EC}{\mathrm{EC}}
\newcommand{\NY}{\mathrm{NY}}
\newcommand{\TT}{\mathrm{TT}}
\newcommand{\REE}{\mathrm{REE}}
\newcommand{\FULL}{\mathrm{FULL}}
\newcommand{\Vol}{\mathrm{Vol}}

% Topology notation
\newcommand{\Sthree}{S^3}
\newcommand{\Tthree}{T^3}
\newcommand{\Nilthree}{\mathrm{Nil}^3}
\newcommand{\Sone}{S^1}

% Differential forms
\newcommand{\wedgep}{\wedge}

% Inner product notation
\newcommand{\innerprod}[2]{\langle #1,\, #2 \rangle}

%------------------------------------------------------------------------------
% Title and authors
%------------------------------------------------------------------------------
\title{Structural Robustness of Isotropic $\Sthree$ Vacua\\
in Einstein--Cartan Minisuperspace\\
via Chiral Equilibrium and Weyl Stability}

\author{Muacca}

\date{}

%==============================================================================
\begin{document}
%==============================================================================

\maketitle
\begin{center}
Version: v1\\
First release: 2026-02-28\\
\end{center}
%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
\begin{abstract}
We examine the robustness of the isotropic $\Sthree\times\Sone$ vacuum
established in our preceding work (paper~I) within the Einstein--Cartan +
Nieh--Yan (EC+NY) Euclidean minisuperspace framework. Two independent
extensions are analysed: a topological one (self-dual instanton decay
paths) and a dynamical one (higher-curvature Weyl-squared corrections).

First, we prove that the Pontryagin density $P=\innerprod{R}{*R}$
vanishes identically under the $M^3\times\Sone$ minisuperspace ansatz
with EC connection---a property we term \emph{chiral equilibrium}---thereby
closing the self-dual instanton decay channel within this framework
(Proposition~1).

Second, we introduce a Weyl-squared term $\alpha\,C^2$ and a
volume-preserving squashed ansatz parameterised by an anisotropy
variable~$\varepsilon$. For $\alpha\le 0$ the conformal flatness
$C^2=0$ of isotropic $\Sthree\times\Sone$ renders the Weyl term inert,
analytically protecting the global minimum of paper~I (Theorem~1). For
$\alpha>0$ the effective potential becomes unbounded below
(Theorem~2). The stability boundary $\alpha=0$ is sharp and independent
of the paper~I matter parameters $(V,\eta,\theta_{\NY})$, a consequence
of the geometric decoupling of the Weyl scalar from torsion
(Theorem~3).

A systematic comparison of three topologies ($\Sthree$, $\Tthree$,
$\Nilthree$) confirms that the topology-selection principle---the
energetic dominance of $\Sthree$---is preserved under the Weyl
extension.
\end{abstract}

%------------------------------------------------------------------------------
% Main text
%------------------------------------------------------------------------------
\input{sections/sec1}   % Introduction
\input{sections/sec2}   % Framework
\input{sections/sec3}   % Chiral Equilibrium
\input{sections/sec4}   % Weyl Extension
\input{sections/sec5}   % Stability (alpha <= 0)
\input{sections/sec6}   % Instability (alpha > 0)
\input{sections/sec7}   % Universality
\input{sections/sec8}   % Topology Comparison
\input{sections/sec9}   % Discussion
\input{sections/sec10}  % Conclusion

%------------------------------------------------------------------------------
% Acknowledgments
%------------------------------------------------------------------------------
\section*{Acknowledgments}

The author acknowledges the use of the following AI tools during manuscript
preparation: Claude Opus 4.6 (Anthropic; accessed 2026-02),
Gemini 3.1 Pro (Google; accessed 2026-02),
Grok 4.2 Beta (xAI; accessed 2026-02), and
GPT-5.2 Thinking via ChatGPT (OpenAI; accessed 2025-12).
These tools were used for language editing (including Japanese--English
translation), outlining and improving exposition, drafting and reviewing
auxiliary code (scripts and pseudocode) that was subsequently tested and
validated by the author, and proposing candidate consistency checks and
alternative derivations to be independently verified by the author. They were
additionally used for literature discovery support (keyword generation and
preliminary summaries of candidate papers); all references and factual claims
were verified by the author using primary sources.

The AI tools did not determine the scientific claims of this work and were not
used to generate or modify research data or evidentiary figures. The author
takes full responsibility for the content and for any remaining errors.

This work was developed within the informal collaborative project
\textbf{DPPU} (\textbf{D}onut-like topology, \textbf{P}lanck-scale
compactness, \textbf{P}recession dynamics, \textbf{U}niverse).

%------------------------------------------------------------------------------
% Appendices
%------------------------------------------------------------------------------
\appendix
\input{appendices/appA}  % DPPUv2 Engine v4 Specification
\input{appendices/appB}  % Numerical Verification Log & Nil³ Analysis
\input{appendices/appC}  % Symbolic Computation Details
\input{appendices/appD}  % Phase Atlas

%------------------------------------------------------------------------------
% References
%------------------------------------------------------------------------------
\bibliographystyle{unsrt}

\begin{thebibliography}{99}

\bibitem{paper1}
Muacca,
``Topology-Dependent Phase Classification of Effective Potentials
in Einstein--Cartan + Nieh--Yan Minisuperspace,''
Zenodo.\ \texttt{10.5281/zenodo.18213677} (2026).

\bibitem{Hehl1976}
F.~W.~Hehl, P.~von der Heyde, G.~D.~Kerlick, and J.~M.~Nester,
``General relativity with spin and torsion: Foundations and prospects,''
Rev.\ Mod.\ Phys.\ \textbf{48}, 393 (1976).

\bibitem{Chandia1997}
O.~Chandia and J.~Zanelli,
``Topological invariants, instantons, and the chiral anomaly on spaces
with torsion,''
Phys.\ Rev.\ D \textbf{55}, 7580 (1997).

\bibitem{NiehYan1982}
H.~T.~Nieh and M.~L.~Yan,
``An identity in Riemann--Cartan geometry,''
J.\ Math.\ Phys.\ \textbf{23}, 373 (1982).

\bibitem{Woodard2015}
R.~P.~Woodard,
``Ostrogradsky's theorem on Hamiltonian instability,''
Scholarpedia \textbf{10}(8), 32243 (2015).

\end{thebibliography}

%==============================================================================
\end{document}
%==============================================================================
